---
title: "IMDb Analysis"
author: "Pritesh Shrivastava"
date: "12/24/2018"
output: html_document
---

We will try to compare the movies of the 3 Khans of Bollywood using the IMDb ratings of their movies as the deciding factor.
IMDb releases it's data publicly in a standard TSV format [here](https://datasets.imdbws.com/). And as expected, these datasets are going to be fairly big in size. 

```{r message=FALSE}
library(tidyverse)
library(magrittr)
```

## Load list of movies
```{r}
movies <- read_csv("movies.csv")
head(movies)
```

## Load movie details
```{r}
movie_details <- read_tsv("title.basics.tsv")
head(movie_details)
```


## Load title rating
```{r}
ratings <- read_tsv("title.ratings.tsv")
head(ratings)
```

## Join the Khan movies with the ratings and the movie details datasets
```{r}
df <- movies %>%
  left_join(ratings) %>%
  left_join(movie_details)

summary(df)
```

### We do not have ratings data for 155 of these movies. Let's filter them out and check the distribution of these movies by actor. Let's also remove irrelevant columns
```{r}
df_clean <- df %>%
  filter(! is.na(averageRating)) %>%
  select(-ordering, -job, -birthYear, -deathYear, -primaryProfession, -knownForTitles, -endYear)

head(df_clean)
```

## Let's check the category field to see if there are movies where the actors did anything other than acting 
```{r}
df_clean %>% group_by(primaryName, category) %>% summarise(count = n())
```

While these 3 have produced very few films so far, the category of self seems to be TV shows, documentaries or other events featuring these celebrites as themselves. 
```{r}
df_clean %>%
  filter(category == "self") %>%
  select(titleType, primaryName, primaryTitle, genres)
```

## We can ignore these from the analysis too.
```{r}
df_clean %<>%
  filter(! category == "self")

glimpse(df_clean)
```

## Let's check the distribution again
```{r}
df_clean %>%
  group_by(primaryName) %>%
  filter(startYear > 2000) %>%
  filter(titleType == "movie") %>%
  summarise(count = n(), 
            meanRating = round(mean(averageRating),1),
            std_dev = round(sd(averageRating),1)) %>%
  ggplot(aes(x = reorder(primaryName, std_dev), y = std_dev, label = meanRating)) +
  geom_col() +
  geom_text(nudge_y = 1) +
  coord_flip() + 
  ylim(0,10) +
    theme_bw()
```

## Let's plot ratings by year 
```{r}
df_clean %>%
  ggplot() +
  geom_line(mapping = aes(x = startYear, y = averageRating, colour = as.factor(primaryName)))
```

## Let's do a histogram
```{r}
df_clean %>%
  filter(primaryName %in% c("Aamir Khan", "Shah Rukh Khan", "Leonardo DiCaprio")) %>%
  ggplot(aes(x = averageRating, fill = as.factor(primaryName))) +
  geom_histogram(alpha = 0.6, position = "identity")
```

